\textbf{Differences in COVID-19 vaccination in the province of Ontario across Health Regions and socio-economic strata}

### 2023-05-08 manuscript_v5/appendix.tex
new directory for version, tidy code

\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Differences in COVID-19 vaccination in the province of Ontario across Health Regions and socio-economic strata},
  pdfauthor={Ariel Mundo Ortiz1,2; Bouchra Nasri1,2,},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, interior hidden, enhanced, breakable, frame hidden, sharp corners]}{\end{tcolorbox}}\fi

@@

\hypertarget{vaccination-rates-by-age}{%
\section{Vaccination rates by Age}\label{vaccination-rates-by-age}}

The table below provides the percentages of vaccination from the survey
data.

\hypertarget{tbl-vaccination}{}
\begin{longtable}{lcc}
\caption{\label{tbl-vaccination}Vaccination Status by Age from the Survey Data }\tabularnewline

\toprule
\textbf{Characteristic} & \textbf{no}, N = 958 & \textbf{yes}, N = 2,591\\
\midrule
\endfirsthead
\multicolumn{3}{@{}l}{\textit{(continued)}}\\
\toprule
\textbf{Characteristic} & \textbf{no}, N = 958 & \textbf{yes}, N = 2,591\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\textbf{Age} &  & \\
\hspace{1em}16 & 11 (21\%) & 41 (79\%)\\
\hspace{1em}17 & 15 (25\%) & 45 (75\%)\\
\hspace{1em}18 & 53 (36\%) & 93 (64\%)\\
\hspace{1em}19 & 33 (31\%) & 74 (69\%)\\
\hspace{1em}20 & 18 (17\%) & 85 (83\%)\\
\hspace{1em}21 & 30 (25\%) & 92 (75\%)\\
\hspace{1em}22 & 19 (23\%) & 62 (77\%)\\
\hspace{1em}23 & 21 (24\%) & 67 (76\%)\\
\hspace{1em}24 & 23 (29\%) & 55 (71\%)\\
\hspace{1em}25 & 25 (24\%) & 80 (76\%)\\
\hspace{1em}26 & 23 (31\%) & 52 (69\%)\\
\hspace{1em}27 & 16 (25\%) & 49 (75\%)\\
\hspace{1em}28 & 13 (20\%) & 52 (80\%)\\
\hspace{1em}29 & 13 (26\%) & 37 (74\%)\\
\hspace{1em}30 & 12 (21\%) & 44 (79\%)\\
\hspace{1em}31 & 17 (38\%) & 28 (62\%)\\
\hspace{1em}32 & 17 (27\%) & 47 (73\%)\\
\hspace{1em}33 & 17 (26\%) & 48 (74\%)\\
\hspace{1em}34 & 33 (35\%) & 60 (65\%)\\
\hspace{1em}35 & 31 (34\%) & 59 (66\%)\\
\hspace{1em}36 & 16 (25\%) & 49 (75\%)\\
\hspace{1em}37 & 15 (30\%) & 35 (70\%)\\
\hspace{1em}38 & 10 (28\%) & 26 (72\%)\\
\hspace{1em}39 & 5 (16\%) & 26 (84\%)\\
\hspace{1em}40 & 7 (16\%) & 36 (84\%)\\
\hspace{1em}41 & 5 (14\%) & 31 (86\%)\\
\hspace{1em}42 & 7 (19\%) & 30 (81\%)\\
\hspace{1em}43 & 9 (17\%) & 45 (83\%)\\
\hspace{1em}44 & 24 (33\%) & 48 (67\%)\\
\hspace{1em}45 & 23 (30\%) & 53 (70\%)\\
\hspace{1em}46 & 13 (24\%) & 41 (76\%)\\
\hspace{1em}47 & 18 (37\%) & 31 (63\%)\\
\hspace{1em}48 & 10 (33\%) & 20 (67\%)\\
\hspace{1em}49 & 8 (28\%) & 21 (72\%)\\
\hspace{1em}50 & 7 (16\%) & 38 (84\%)\\
\hspace{1em}51 & 7 (23\%) & 23 (77\%)\\
\hspace{1em}52 & 9 (20\%) & 36 (80\%)\\
\hspace{1em}53 & 9 (22\%) & 31 (78\%)\\
\hspace{1em}54 & 19 (37\%) & 33 (63\%)\\
\hspace{1em}55 & 12 (23\%) & 41 (77\%)\\
\hspace{1em}56 & 13 (26\%) & 37 (74\%)\\
\hspace{1em}57 & 12 (22\%) & 43 (78\%)\\
\hspace{1em}58 & 6 (14\%) & 37 (86\%)\\
\hspace{1em}59 & 4 (12\%) & 28 (88\%)\\
\hspace{1em}60 & 3 (11\%) & 25 (89\%)\\
\hspace{1em}61 & 1 (4.5\%) & 21 (95\%)\\
\hspace{1em}62 & 8 (26\%) & 23 (74\%)\\
\hspace{1em}63 & 5 (19\%) & 21 (81\%)\\
\hspace{1em}64 & 11 (33\%) & 22 (67\%)\\
\hspace{1em}65 & 11 (20\%) & 45 (80\%)\\
\hspace{1em}66 & 11 (28\%) & 28 (72\%)\\
\hspace{1em}67 & 8 (22\%) & 28 (78\%)\\
\hspace{1em}68 & 5 (19\%) & 21 (81\%)\\
\hspace{1em}69 & 17 (39\%) & 27 (61\%)\\
\hspace{1em}70 & 4 (14\%) & 24 (86\%)\\
\hspace{1em}71 & 1 (3.8\%) & 25 (96\%)\\
\hspace{1em}72 & 2 (9.1\%) & 20 (91\%)\\
\hspace{1em}73 & 3 (12\%) & 22 (88\%)\\
\hspace{1em}74 & 13 (31\%) & 29 (69\%)\\
\hspace{1em}98 & 147 (42\%) & 201 (58\%)\\*
\multicolumn{3}{l}{\rule{0pt}{1em}\textsuperscript{1} n (\%)}\\
\end{longtable}

>>>>

\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{placeins}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Differences in COVID-19 vaccination in the province of Ontario across Health Regions and socio-economic strata},
  pdfauthor={Ariel Mundo Ortiz1,2; Bouchra Nasri1,2,},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, sharp corners, breakable, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden]}{\end{tcolorbox}}\fi

@@

\hypertarget{complete-model-estimates}{%
\section{Complete Model Estimates}\label{complete-model-estimates}}

The figures below present the complete estimates from the regression
models.

\includegraphics{appendix_files/figure-pdf/fig-model-uncorr-appendix-1.pdf} \hfill{}

\caption{\label{fig-model-uncorr-appendix}Full coefficient estimates and
confidence intervals for the uncorrected model.}

\FloatBarrier

\includegraphics{appendix_files/figure-pdf/fig-model-corr-appendix-1.pdf} \hfill{}

\caption{\label{fig-model-corr-appendix}Full coefficient estimates and
confidence intervals for the corrected model.}

\FloatBarrier

### 2023-05-08 manuscript_v5/main.qmd
new directory for version, tidy code

library(weights)
library(here)
library(survey)
library(magrittr)
library(tidyverse)
library(lme4)
library(lubridate)
library(kableExtra)
library(modelsummary)
library(gtsummary)
library(patchwork)
```

>>>>

library(weights)
library(here)
library(survey)
library(magrittr)
library(tidyverse)
library(naniar)
library(lme4)
library(lubridate)
library(kableExtra)
library(modelsummary)
library(gtsummary)
library(patchwork)
```

### 2023-05-08 manuscript_v5/main.tex
new directory for version, tidy code

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden, interior hidden, enhanced, boxrule=0pt, sharp corners]}{\end{tcolorbox}}\fi

@@

Preliminary analyses of the data included the removal of outliers, of
observations where respondents did not provide answers in all the
covariates of interest, matching the city of each observations with its
corresponding LHIN and Health Region, and removing observations from
areas with low representation (107 observations corresponding to the
North West and North East Health Regions). After all the preliminary
analyses indicated above, the total number of observations used for
analysis was 3,549 which included the East, Central, Toronto, and West
Health Regions covering the period between October 1st,2021 and December
12th, 2021. The original dataset, clean dataset, and details on the data
cleaning process are described in detail in the
\href{https://github.com/aimundo/Fields_COVID-19/}{GitHub repository}
for this paper.

@@

Comparisons between the variables of the survey were performed using the
\(\chi^2\) test. We used a logistic regression model to examine the
impact of the Health Regions in vaccination rates while considering the
socio-economic factors and and months covered by the survey
(Table~\ref{tbl-descriptive-stats}) and certain interactions (Race and
Health Region and Race and income), as previous studies have shown that
socio-economic factors and their interactions are significant predictors
of intent of vaccination and vaccination
status\textsuperscript{\protect\hyperlink{ref-nguyen2022}{32}--\protect\hyperlink{ref-cnat2022a}{34}}.
Because we identified differences in representativity between the survey
data and the estimates from the Census, we used an iterative
proportional fitting procedure
(\emph{raking})\textsuperscript{\protect\hyperlink{ref-deming1940}{35}}
to correct the data using data from the Census and Health Region
population totals; and fitted the regression model to the uncorrected
and corrected data. The reference groups in the model were: 16-34 years
(age group), October(Month), CAD 60,000 and above (income),
White/Caucasian (Race), Toronto (Health Region). Details regarding the
correction can be found in the Appendix. All analyses were conducted in
R 4.2.2 using the packages
\texttt{survey}\textsuperscript{\protect\hyperlink{ref-lumley2011}{36}},\texttt{tidyverse}\textsuperscript{\protect\hyperlink{ref-wickham2019}{37}},
\texttt{quarto}\textsuperscript{\protect\hyperlink{ref-quarto}{38}},
\texttt{modelsummary}\textsuperscript{\protect\hyperlink{ref-modelsummary}{39}},
and
\texttt{gtsummary}\textsuperscript{\protect\hyperlink{ref-gtsummary}{40}}.

@@

Table~\ref{tbl-descriptive-stats} shows the characteristics of the data
from the Fields COVID-19 survey used for analysis with regard to
vaccination status. A total of 3,549 observations were used for
analysis, from which 27\% (958) corresponded to individuals that
reported not having received the first dose of the vaccine. Respondents
between 16 and 34 years of age, and those that lived within the Health
Region of Toronto had the highest number of observations in the data
(42.8\% and 37.3\% of the total, respectively). Moreover, individuals
who identified as White or Caucasian reported the highest vaccination
uptake (82\%), in contrast to respondents who identified as which had
had the lowest vaccination uptake rate (60\%) across all groups. From
all the covariates, significant associations were identified between
income, race, and vaccination rate.

@@

\toprule
\textbf{Variable} & \textbf{no}, N = 958\textsuperscript{1} & \textbf{yes}, N = 2,591\textsuperscript{1} & \textbf{p-value}\textsuperscript{2} \\ 
\midrule
Income (CAD) &  &  & <0.001 \\ 
    60000 and above & 305 (23\%) & 1,048 (77\%) &  \\ 
    25000-59999 & 253 (28\%) & 636 (72\%) &  \\ 
    under 25000 & 400 (31\%) & 907 (69\%) &  \\ 
Age Group &  &  & 0.7 \\ 
    16-34 & 409 (27\%) & 1,111 (73\%) &  \\ 
    35-54 & 252 (26\%) & 712 (74\%) &  \\ 
    55 and over & 297 (28\%) & 768 (72\%) &  \\ 
Health Region &  &  & 0.14 \\ 
    Toronto & 371 (28\%) & 952 (72\%) &  \\ 
    Central & 224 (28\%) & 580 (72\%) &  \\ 
    East & 135 (23\%) & 448 (77\%) &  \\ 
    West & 228 (27\%) & 611 (73\%) &  \\ 
Month &  &  & 0.4 \\ 
    October & 469 (27\%) & 1,263 (73\%) &  \\ 
    November & 376 (28\%) & 980 (72\%) &  \\ 
    December & 113 (25\%) & 348 (75\%) &  \\ 
Race &  &  & <0.001 \\ 
    White/Caucasian & 233 (18\%) & 1,079 (82\%) &  \\ 
    Arab/Middle Eastern & 76 (36\%) & 138 (64\%) &  \\ 
    Black & 114 (38\%) & 184 (62\%) &  \\ 
    East Asian/Pacific Islander & 69 (23\%) & 234 (77\%) &  \\ 
    Indigenous & 76 (40\%) & 115 (60\%) &  \\ 
    Latin American & 69 (38\%) & 111 (62\%) &  \\ 
    Mixed & 105 (34\%) & 205 (66\%) &  \\ 
    Other\textsuperscript{3} & 128 (35\%) & 239 (65\%) &  \\ 
    South Asian & 88 (24\%) & 286 (76\%) &  \\ 
\bottomrule
\end{longtable}
\begin{minipage}{\linewidth}
\textsuperscript{1}n (\%)\\
\textsuperscript{2}Pearson\textquotesingle{}s Chi-squared test\\
\textsuperscript{3}Southeast Asian, Filipino, West Asian,
and minorities not identified elsewhere according to the Census.\\
\end{minipage}

>>>>

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, boxrule=0pt, interior hidden, breakable, borderline west={3pt}{0pt}{shadecolor}, sharp corners, frame hidden]}{\end{tcolorbox}}\fi

@@

Preliminary analyses of the data included the removal of outliers
(\textbf{should we still do this? it's only 19 observations with income
\textgreater110k and household of 1, but we are not even using such
income bracket in the analysis because we re-grouped the data, and the
household size variable has 90\% missing rate}), of observations where
respondents did not provide answers in all the covariates of interest,
matching the city of each observations with its corresponding LHIN and
Health Region, and removing observations from areas with low
representation (107 observations corresponding to the North West and
North East Health Regions). After all the preliminary analyses indicated
above, the total number of observations used for analysis was 3,549
which included the East, Central, Toronto, and West Health Regions
covering the period between October 1st,2021 and December 12th, 2021.
The original dataset, clean dataset, and details on the data cleaning
process are described in detail in the
\href{https://github.com/aimundo/Fields_COVID-19/}{GitHub repository}
for this paper.

@@

We used a logistic regression model to examine the impact of the Health
Regions in vaccination rates while considering the socio-economic
factors and and months covered by the survey
(Table~\ref{tbl-descriptive-stats}) and certain interactions (Race and
Health Region and Race and income), as previous studies have shown that
socio-economic factors and their interactions are significant predictors
of intent of vaccination and vaccination
status\textsuperscript{\protect\hyperlink{ref-nguyen2022}{32}--\protect\hyperlink{ref-cnat2022a}{34}}.
Because we identified differences in representativity between the survey
data and the estimates from the Census, we used an iterative
proportional fitting procedure
(\emph{raking})\textsuperscript{\protect\hyperlink{ref-deming1940}{35}}
to correct the data using data from the Census and Health Region
population totals; and fitted the regression model to the uncorrected
and corrected data. Details regarding the correction can be found in the
Appendix. All analyses were conducted in R 4.2.2 using the packages
\texttt{survey}\textsuperscript{\protect\hyperlink{ref-lumley2011}{36}},\texttt{tidyverse}\textsuperscript{\protect\hyperlink{ref-wickham2019}{37}},
\texttt{quarto}\textsuperscript{\protect\hyperlink{ref-quarto}{38}},
\texttt{modelsummary}\textsuperscript{\protect\hyperlink{ref-modelsummary}{39}},
and
\texttt{gtsummary}\textsuperscript{\protect\hyperlink{ref-gtsummary}{40}}.

@@

Table~\ref{tbl-descriptive-stats} shows the characteristics of the data
from the Fields COVID-19 survey used for analysis with regard to
vaccination status. A total of \textbf{6,236} observations were used for
analysis, from which 24\% (1,547) corresponded to individuals that
reported not having received the first dose of the vaccine. Across the
socio-demographic characteristics collected by the survey, higher
vaccination uptake was reported by individuals in the highest income
bracket considered, those between 16 and 34 years of age, individuals
that lived in the East Health Region, and individuals that identified as
White or Caucasian. During the months covered by the survey, the highest
vaccination uptake was observed in January of 2022.

@@

\toprule
\textbf{Variable} & \textbf{no}, N = 1,547\textsuperscript{1} & \textbf{yes}, N = 4,689\textsuperscript{1} & \textbf{p-value}\textsuperscript{2} \\ 
\midrule
Income (CAD) &  &  & <0.001 \\ 
    60000 and above & 542 (21\%) & 1,996 (79\%) &  \\ 
    25000-59999 & 347 (25\%) & 1,046 (75\%) &  \\ 
    under 25000 & 658 (29\%) & 1,647 (71\%) &  \\ 
Age Group &  &  & 0.002 \\ 
    16-34 & 645 (23\%) & 2,117 (77\%) &  \\ 
    35-54 & 411 (24\%) & 1,305 (76\%) &  \\ 
    55 and over & 491 (28\%) & 1,267 (72\%) &  \\ 
Health Region &  &  & 0.3 \\ 
    Toronto & 593 (26\%) & 1,709 (74\%) &  \\ 
    Central & 372 (26\%) & 1,083 (74\%) &  \\ 
    East & 236 (23\%) & 783 (77\%) &  \\ 
    West & 346 (24\%) & 1,114 (76\%) &  \\ 
Month &  &  & <0.001 \\ 
    October & 469 (27\%) & 1,263 (73\%) &  \\ 
    November & 376 (28\%) & 980 (72\%) &  \\ 
    December & 181 (24\%) & 565 (76\%) &  \\ 
    January & 521 (22\%) & 1,881 (78\%) &  \\ 
Race &  &  & <0.001 \\ 
    White/Caucasian & 354 (16\%) & 1,871 (84\%) &  \\ 
    Arab/Middle Eastern & 111 (34\%) & 220 (66\%) &  \\ 
    Black & 159 (34\%) & 303 (66\%) &  \\ 
    East Asian/Pacific Islander & 94 (19\%) & 404 (81\%) &  \\ 
    Indigenous & 112 (37\%) & 194 (63\%) &  \\ 
    Latin American & 99 (34\%) & 195 (66\%) &  \\ 
    Mixed & 177 (30\%) & 411 (70\%) &  \\ 
    Other\textsuperscript{3} & 315 (34\%) & 606 (66\%) &  \\ 
    South Asian & 126 (21\%) & 485 (79\%) &  \\ 
\bottomrule
\end{longtable}
\begin{minipage}{\linewidth}
\textsuperscript{1}n (\%)\\
\textsuperscript{2}Pearson\textquotesingle{}s Chi-squared test\\
\textsuperscript{3}Southeast Asian, Filipino, West Asian,
and minorities not identified elsewhere according to the Census.\\
\end{minipage}
